\documentclass{resume}
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage[svgnames]{xcolor}
\usepackage{hyperref}
\hypersetup{%
  colorlinks=true,          % hyperlinks
  allcolors=DarkRed,%
  pdfborderstyle={/S/U/W 1}, % border style will be underline of width 1pt
    pdfcreator={Shangjie Zhou}
  }

\usepackage{vwcol}
\usepackage{cfr-lm}         % make old style numbers default
\usepackage{graphicx}


\newcommand{\myname}[1]{\textbf{Shangjie Zhou}}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE SECTION
\begin{center}
    \name{Shangjie Zhou}
    \contact
    {\normalsize +86-181-7299-8689}
    {\normalsize\href{mailto:sjzhou@whu.edu.cn}{sjzhou@whu.edu.cn}}
    {\normalsize\href{http://zhou-shangjie.com/}{zhou-shangjie.com}}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION 
\section{Education}
\begin{content}

    {\href{https://www.whu.edu.cn}{\bf Wuhan University}} \hfill {\bf Sept. 2019 -- June 2023 (expected)} \\
    {\bf B.S. in Physics}, \href{https://physics.whu.edu.cn}{School of Physics and Technology} \& \href{https://hyxt.whu.edu.cn}{Hongyi Honor College} \hfill Hubei, China\\
    {\em Hongyi Honor Program}

    % \vspace{-.25\baselineskip}
    % {\em Honours:} If you'd rather list your awards here than in a separate section later, simply write the awards here and comment out that section (and vice versa).
    \sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH EXPERIENCE
\section{Research Experience}
\begin{content}

    \begin{position}{Gravitational Lensing Group}{May 2021 -- Present}{Undergraduate Research}{Prof.~\href{https://physics.whu.edu.cn/info/1053/2152.htm}{Junji Jia}}{\href{https://physics.whu.edu.cn}{School of Physics and Technology}, \href{https://www.whu.edu.cn}{Wuhan University}}
        \item Literature reading.
        \item Studying gravitational lensing effect using perturbative method.
        \item General relativity seminar.
    \end{position}
    \vspace{-.5\baselineskip}

    \begin{position}{Scattering Amplitude Group}{Nov. 2021 -- Present}{Undergraduate Research}{Prof.~\href{https://physics.whu.edu.cn/info/1053/2130.htm}{Yi-Jian Du}}{\href{https://physics.whu.edu.cn}{School of Physics and Technology}, \href{https://www.whu.edu.cn}{Wuhan University}}
        \item Literature reading.
        \item Studying scattering amplitudes from the perspective of \textit{color-kinematic dulity}.
        \item Quantum field theory seminar.
    \end{position}
    \vspace{-.5\baselineskip}

    \begin{position}{Holographic Entangle Entropy Group}{Jul. 2022 -- Present}{Research Assistant}{Prof.~\href{https://yauc.seu.edu.cn/wq1_33668_en/list.htm}{Qiang Wen}}{\href{https://yauc.seu.edu.cn/}{Shing-Tung Yau Center} and \href{https://math.seu.edu.cn/}{School of Mathematics}, \href{https://www.seu.edu.cn/}{Southeast University}}
        \item Literature reading.
        \item Studying Island formula in Information Paradox.
    \end{position}
    \vspace{-.5\baselineskip}
    \sectionlineskip
\end{content}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PUBLICATIONS 
\noindent
\renewcommand{\refname}{Publications}   % name of the reference section
\bibliography{biblio.bib}
\bibliographystyle{jhep}          % citation style
\nocite{*}
\sectionlineskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AWARDS
\section{Awards}
\begin{content}
    \prize{Merit-Based Second Class Scholarship}{Oct. 2021}{\textit{Wuhan University}}

    \prize{Hongyi Academic Scholarship}{Oct. 2020}{\textit{Hongyi Honor College}}
    \sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROJECTS
\section{Projects \& Extracurriculars}
\begin{content}


    \begin{position}{Seminars on Geometry, Topology and Physics}{Jan. 2022 -- Present}{Co-organizer}{}{}
        \item Weekly seminar on geometry and topology following the book \textit{Geometry, Topology and Physics} by \textit{Mikio Nakahara}.
        \item Notes available online (under construction): \url{https://physicswhu.github.io/Nakahara-Notes}.
    \end{position}


    \sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TECHNICAL SKILLS
\section{Technical Skills}
\begin{content}
    \begin{tabular}{ @{} >{\bf}l @{\hspace{6ex}} l }
        Programming Languages & C ,Python, \LaTeX\                       \\
        Tools \& Software     & MATLAB, Wolfram Mathematica              \\
        Languages             & Mandarin (native), English (professional) \\
        TOEFL                 & 100                                      \\
        GRE                   & V 154+ Q 170+ AWA 3.5
    \end{tabular}
    \sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% COURSE WORK
\section{Selected Course Work}
\begin{tabular}{l l l}
    \qquad {\bf Mathematics}     & \qquad {\bf Physics} & \qquad {\bf Physics}       \\[.5\smallskipamount]

    Calculus                     & Classical  Mechanics & Solid State Physics        \\
    Linear Algebra               & Statistical Physics  & Particle Physics           \\
    Probability Theory           & Electrodynamics      & Advanced Quantum Mechanics \\
    Ordinary Diffential Equation & Quantum Mechanics    & Quantum Field Theory
\end{tabular}

\begin{center}
    \vfill
    \textit{Last updated on: \today}
\end{center}
\end{document}
